Cannibalism among the supermassive black holes

### 2018-05-18 paper.tex
Made some more changes.

\subsection{Overview of simulation}
Our simulations focused on elliptical galaxies with central SMBHs. The galaxies were given a background potential based on the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.  The galaxies were evolved between $0 < z < 4$.  Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed.

@@

@@

Starting with this data, we plotted the galaxy masses as a function of time.  Since the raw data was given in terms of redshift, we converted redshift to time.  We chose four galaxies to run our simulations.  The galaxies were chosen using the following basic criteria:
\begin{itemize}
\item The galaxies had to exist through the entire simulation ($0 < z < 4$).
\item They had to have a central SMBH.
\item They had to have at least XXX orbiting black holes.
\item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.  We chose the four largest galaxies that also satisfied the above criteria.
\end{itemize}

@@

\subsubsection{Galaxy background potential}
The simulations from which we obtained the merger tree data considered only dark matter distributions and were run using the Navarro-Frenk-White (NFW) profile \citet{1997ApJ...490..493N}.  Since our study is more interested SMBH mergers at the center of galaxies, dynamical friction, and hence baryonic matter, was of considerable importance.  Therefore, the NFW background potential was less suitable for our application.

>>>>

\subsection{Overview of simulation}
Our simulations focused on elliptical galaxies with central SMBHs. The galaxies were given a background potential based on the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.  The galaxies were evolved between $0 < z < 4$.  Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed, as described further below.

@@

The merger tree data from Lackner12 and Kulier15 provided 1,830 galaxies in total.  However, not all the galaxies were useful for our simulations.  We placed further:
\begin{itemize}
\item The galaxies had to exist through the entire simulation ($0 < z < 4$).
\item They had to have a central SMBH.
\item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.  We chose the four largest galaxies that also satisfied the above criteria.
\end{itemize}

@@

@@

\subsubsection{Galaxy background potential}
The simulations from which we obtained the merger tree data were run using the Navarro-Frenk-White (NFW) profile \citet{1997ApJ...490..493N}.  Since our study is more interested SMBH mergers at the center of galaxies, dynamical friction, and hence baryonic matter, was of considerable importance.  Therefore, the NFW background potential was less suitable for our application.
